---
title: 'Analysis of the City of Toronto Tickets Infractions '
output:
  html_notebook: default
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

**By Mohammad AL-Amar**






*3.1.1 The top 20 ticket infractions by frequency*

Data contains the infaction's code, description and frequency

```{r}
top_20_frequency
```
*3.1.2 The top 20 ticket infractions by revenue*

Data contains the infaction's code, description and total revenue

```{r}
top_20_revenue
```
*3.1.3 Total revenue for the top 20 ticket infractions*
```{r}
total_revenue
```
*3.1.4 The closest parking lot (Green P) to each of the top 20 infraction locations*

Data contains ticket infraction's location, frequencey, closest parking distance by meter, parking ID and parking address

```{r}
closest_parking_to_infraction_locations
```
*3.1.4b The closest TTC stop to each of the top 20 infraction locations*

Data contains ticket infraction's location, frequencey, closest TTC stop distance by meter, stop ID and TTC stop name

```{r}
closest_TTC_stop_to_infraction_locations
```

*3.1.5a The impact of Day of week  on all infractions *

Data contains Day of  week, frequencey

```{r}
infractions_day_of_week
```
*3.1.5b The impact of Month on all infractions *

Data contains Day of  week, frequencey

```{r}
         
infractions_month
```
*3.1.5b The impact of Season on all infractions *

Data contains Season, frequencey

```{r}
infractions_Season
```
*3.3.1.ai The Distribution of all infractions by Year  *


```{r}
infractions_by_year
```


*3.3.1.aii The Distribution of all infractions by Month  *
```{r}
infractions_by_month
```

*3.3.1.b The Distribution of top 20 infractions by total ticket fines  *
```{r}
infractions_by_fines
```


*3.3.2.a The Distribution of top 20 infractions Location  *


```{r}

Location
```
*3.3.2.b The Distribution of top 20 infractions count ward  *

```{r}
Count_by_ward
```


*3.3.2.c The Distribution of top 20 infractions sum fines by ward  *
```{r}


Fines_by_ward
```




